Ring of Fire Camera Detections Report

### 2023-02-27 analysis/paper/paper.qmd
updates

events_rda <- vegan::rda(vegan::decostand(events_tb_cam, "hellinger") ~ .,
                         extr_table_sub_tb)

@@

>>>>

events_tb_cam_hell <- vegan::decostand(events_tb_cam, "hellinger")

events_rda <- vegan::rda( events_tb_cam_hell ~ .,
                         extr_table_sub_tb)

# vegan::RsquareAdj(events_rda)

@@

### Clustering

```{r}
clust <- hclust(cluster::daisy(events_tb_cam_hell, "gower"), 
                method = "ward.D2")
plot(clust)
```

```{r}
clust_grp <- cutree(clust, k=5)
custom_rda_plot(events_rda, sp_scale = 1.5, clust = clust_grp)
```
